BurgerMax Presents: OpenAdcess

### 2017-03-01 related-work.tex
Hecka citations
More wisdom

\todo{Harvest paper} and many other free rags employ heavy use of in paper ads,
native ads, and classifieds.
We also adopt these techniques to embed in all of our papers in
\autoref{sec:sponsors}.

>>>>

Wisdom \cite{wisdom} and many other free rags employ heavy use of in paper ads,
native ads, and classifieds.
We also adopt these techniques to embed in all of our papers in
\autoref{sec:sponsors}.
Additionally, Wisdom claims most holism but we have the narrow computational
tools to prove that we are more holistic.
